Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-30 docs/ms.tex
Update ms.tex

\section{Discussion}
\label{sec:XXX}

>>>>

\section{Discussion}
\label{sec:XXX}
In weak lensing survey,one way to obtain high S/N ratio is to stack large number of lensing signal together,and 
calculate the mean shear map of all these lensing systems.However simply to stack allthe lensing signals would not be the
optimal way because of the amount of information we can obtain from each lensing system can be very different.
The Bayesian inference approach we proposed allows a natural way to optimally include all the data.In stead of stacking what we need to do
is to propogate the likelihood of the shear map of each lensing system. The statistical property of all the lensing systems
like the galaxy-mass ,shear-shar correlation function ,in principle can be calculated from these likelihood functions.
